Senior Experience Reflective Essay

### 2017-05-17 papers/essay.tex
Adds reflective essay

• What else have you learned about yourself? About your project topic?
• Is the project topic something you are likely to pursue once senior projects are over?
• Without a quiz, paper, test, homework assignment or teacher to motivate you, what has
motivated you to work on your senior project this week? Is it purely getting through the
last graduation requirement, or do you truly enjoy spending time on this project that you
created? Is it hard to motivate yourself to spend time on the project? Write some ideas
about what motivates you.
• If your project were a class and you were the teacher, how would you assess/test/evaluate
your students’ progress, understanding, skill? Would you give a written test based on
knowledge, a hands-on demonstration of skill, or some other evaluation?
• If you made a soundtrack to your senior project, what songs would you include and why?
• Describe a metaphor for this experience. Fill in the blank and elaborate: This experience
has been like...
• What advice would you give next year’s seniors?

% ==================================================
\section{Appendix}
% ==================================================

>>>>

During this project, I've read more than 30 publications: From Bell Labs, Sandia Labs, Los Alamos Labs, Harvard, Carnegie Mellon, MIT, IBM, NASA, and Microsoft.
For every problem I've solved, I've probably found another dozen that are worth pursuing.
Quantum Computing is a vast field, and I'm lucky to have been exposed to even a small percentage of it.

As this project comes to a close, I feel that I've gained a layprogrammers perspective of running NP-Complete problems on different types of Quantum Computers.
Since I'm unaffiliated with either IBM, Los Alamos, or DWave, I've been able to approach the problem from a neutral perspective, and recognize both the flaws and benefits of each implementation.
In addition, I've grown close to the problem itself. I see instances of it in my daily life, and am continually impressed by how subtle it is.
For instance, while I was completing my senior experience I was simultaneously hunting craigslist for used cars.
I wanted to find a car with good mileage, high safety, enjoyable peripherals (like a stereo), and a low odometer reading, for the lowest price possible.

Surprisingly, this is essentially an instance of the knapsack problem! 
At home, at school, and in business, the Knapsack problem shows up.
I appreciate the importance of solving this problem using Quantum Computation, and will be continuing my research with Los Alamos if possible, as well as working on similar problems at Sandia.
